---
title: "ENGG 21 Final Project"
author: "Calpito, Casenas, de Leon, Lorenzo, Oba"
date: 'July 21, 2022'
output: 
  html_document:
      code_folding: "show"
      theme: united
---
# Correlation of CPU Price and Performance

## Introduction
(to be added later)

## Methodology
(to be added later)
<<<<<<< HEAD
=======

## Results
The price and CPU mark (measured by Passmark) of 1,967 different CPUs were analyzed in this study. Here's a scatter plot to visualize:

```{r warning=FALSE, message=FALSE, fig.align='center'}
library(tidyverse)

cpuData<-read.csv("CPU_benchmark_v4.csv")

cpuData %>% ggplot(aes(x = cpuMark, y = price)) + geom_point()+ theme_bw()

```



In this analysis, the correlation between CPU price and performance will be tested with α= 0.05 (95% confidence interval). 
>>>>>>> b3a9752591d3131712b3834ba42e3edc9997ad14

## Results
|           The price and CPU mark (measured by PassMark) of 1,967 different CPUs were analyzed in this study. Through simple linear regression, the following regression model is obtained:
```{r warning=FALSE, message=FALSE, fig.align='center'}
cpuData<-read.csv("CPU_benchmark_v4.csv")
model<-lm(cpuData$price~cpuData$cpuMark)
plot(x = cpuData$cpuMark, y = cpuData$price, main="CPU Mark vs Price", xlab="cpu mark", ylab="price")
abline(model, col=2, lwd=3)

```
<center>
#### $Price = -26.0569634 + 0.0580751*(CPU Mark)$
</center>

|           In this analysis, this model of correlation will be tested with significance level α = 0.05 (95% confidence interval). 



## Discussion
(to be added later)

## Conclusion
(to be added later)

## Reference
(to be added later)