---
title: "ENGG 21 Final Project"
author: "Calpito, Casenas, de Leon, Lorenzo, Oba"
date: 'July 21, 2022'
output: 
  html_document:
      code_folding: "show"
      theme: united
---
# Correlation of CPU Price and Performance

## Introduction
(to be added later)

## Methodology
(to be added later)

## Results

---
|           <font size="3">The price and CPU mark (measured by PassMark) of 1,967 different CPUs were analyzed in this study. Through simple linear regression, the following regression model is obtained:
```{r warning=FALSE, message=FALSE, fig.align='center'}
cpuData<-read.csv("CPU_benchmark_v4.csv")
model<-lm(cpuData$price~cpuData$cpuMark)
plot(x = cpuData$cpuMark, y = cpuData$price, main="CPU Mark vs Price", xlab="cpu mark", ylab="price")
abline(model, col=2, lwd=3)

```
<center>
#### $Price = -26.0569634 + 0.0580751*(CPU Mark)$
</center>
|           The Pearson correlation coefficient and r-squared are: 
```{r}
r=cor(cpuData$cpuMark, cpuData$price)
sprintf("r = %f", r)
sprintf("r-squared = %f", r^2)

```
|           This model of correlation will be tested with significance level α = 0.05 (95% confidence interval). The test goes as follows:

<ul>
<li>Null Hypothesis $H_0$: $β_0=0$</li>
<li>Alternative Hypothesis $H_1$: $β_0\neq0$</li>
<li>Test Statistic: </li>
<center>$F=\frac{\frac{{\rm RSS}_R-{\rm RSS}_{UR}}{\rho_{fit}-\rho_{mean}}}{\frac{{\rm RSS}_{UR}}{n-\rho_{fit}}}$ </center>
<li> We reject $H_0$ if $F>F_{0.05,1965}$
```{r}
F=qf(0.05, 1, 1965, lower.tail = FALSE)
sprintf('F_{0.05,1965} = %f',F)
```
Therefore, we reject $H_0$ if $F>3.846196$.</li>
</ul>

**Calculation:**
```{r}
summary(model)
```
|           The F-statistic is calculated to be 1812 which is far greater than 3.846. Therefore, we reject $H_0$. 
</font>

#### **Residual Analysis**
```{r warning=FALSE, message=FALSE, fig.align='center'}
library(ggfortify)
autoplot(object = model) + theme_classic()
```

|           Looking at the Residuals vs Fitted plot, we see a very slight upward concavity on the line. In the normal Q-Q plot, a lot of residuals are seen to deviate away from the line especially on the far right.

## Discussion
(for r pearson correlation coefficient)This shows a low to moderate positive correlation between CPU Mark and price.
(for F statistic) The correlation between CPU mark and price is statistically significant (with alpha 0.05).

(residual analysis) change in the variation within the 1000-3000 CPU Mark, (the model predicts slightly higher than what the actual data suggests)

doesn't follow normal distribution as there are lots of "outliers" as CPU Marks go up (data points that deviate going higher than the model predicts)

## Conclusion
(to be added later)

## Reference
(to be added later)